### 2016-07-06 lineups.Rnw
why dplyr, whyyyyyy???? :'(

lus_summary_2 <- lus_spread %>% group_by(part, lineupid, param_name) %>%
  summarize(
    data_n = sum(true_model=="M2"),
    data_est = mean(M2[true_model=="M2"]),
    data_sd = sd(M2[true_model=="M2"], na.rm=TRUE),
    null_est = list(M2[true_model=="M1"]),
    data_dist = data_est - max(unlist(null_est)),
    upper_qu = sum(data_est > unlist(null_est))/(n()-1)
  )

>>>>

lus_summary_2 <- lus_spread %>% group_by(part, lineupid, param_name) %>%
  summarize(
    data_n = sum(true_model=="M2"),
    data_est = mean(M2[true_model=="M2"]),
    data_sd = sd(M2[true_model=="M2"], na.rm=TRUE),
    null_est = list(M2[true_model=="M1"]),
    #data_dist = data_est - max(unlist(null_est)),
    #upper_qu = sum(data_est > unlist(null_est))/(n()-1)
  )
# XXX The lines commented out above crash my RStudio. I haven't figured out why yet! :( XXX
